Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-10-29 Report/mse_formulation.tex
final modifications
Updated draft with boundedness argument

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receive beamformers. The optimization subproblem to find the transmit precoders for fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}. The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.

>>>>

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receive beamformers. The optimization subproblem to find the transmit precoders for fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.

In all simulations, the objective of Algorithm \ref{algo-1} converges. \reviewF{However, to discuss the theoretical convergence of subproblems \eqref{eqn-9}, \eqref{eqn-9--1} and \eqref{eqn-mse-2}, following modifications are considered. (i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective with quadratic term as in \eqref{mod_obj} to ensure strong convexity in objective function. (ii) To guarantee the boundedness of feasible sets, we trivially bound \eqn{\beta_{l,k,n}}'s and \eqn{\mvec{w}{l,k,n}}'s as \eqn{\beta_{l,k,n} \leq P_{\max}} and \eqn{\|\mvec{w}{l,k,n}\|^2 \leq 1} in subproblems \eqref{eqn-9} and \eqref{eqn-9--1}. However, these additional constraints on optimization variables has no impact on final solution or objective. Using this, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}

### 2015-10-29 Report/wsrm_formulation.tex
final modifications
Updated draft with boundedness argument

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}. For brevity, let us consider \eqn{\mbf{m}} as the collection of all transmit precoders in the system as \eqn{\mbf{m} = \{\mvec{m}{l,k,n}\}_{\forall l,\forall k, \forall n}}. Similarly, we denote \eqn{\mbf{w}} and \eqn{\mbfa{\beta}} as \eqn{\{\mvec{w}{l,k,n}\}_{\forall l,\forall k, \forall n}} and \eqn{\{\mvec{\beta}{l,k,n}\}_{\forall l,\forall k, \forall n}} respectively. Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution of \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step. Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\lpointx}, \mbfa{\beta}^{(i)}_{j} \}}. Note that \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is the receiver, which is obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq K_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr} and increment $j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}

Upon convergence of the objective sequence, the receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from the previous \ac{SCA} step. Once the receive beamformers are updated, the transmit precoders are again evaluated with the newly found receivers by solving \eqref{eqn-9} recursively or by using \eqref{eqn-10}. The above procedure is repeated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations as outlined in Algorithm \ref{algo-1}.

The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying the total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained with the corresponding \ac{MMSE} receivers in \eqref{eqn-10}. Now, by using the fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c} for all the users in the system.

Note that in all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges. \reviewF{However, to analyze the convergence of the sequence of beamformer iterates}, we consider modified objective \eqref{mod_obj} with a quadratic term instead of \eqref{eqn-6.1}. Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.
\begin{comment}

>>>>

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find transmit precoders by solving \eqref{eqn-9}. For brevity, let us consider \eqn{\mbf{m}} as the collection of all transmit precoders as \eqn{\mbf{m} = \{\mvec{m}{l,k,n}\}_{\forall l,\forall k, \forall n}}. Similarly, we denote \eqn{\mbf{w}} and \eqn{\mbfa{\beta}} as \eqn{\{\mvec{w}{l,k,n}\}_{\forall l,\forall k, \forall n}} and \eqn{\{\mvec{\beta}{l,k,n}\}_{\forall l,\forall k, \forall n}} respectively. Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution of \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step. Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\lpointx}, \mbfa{\beta}^{(i)}_{j} \}}. Note that \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is obtained by solving either \eqref{opt-rx} or by using \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq K_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr} and increment $j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}

Upon convergence of objective sequence, receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from previous \ac{SCA} step. Once the receivers are updated, transmit precoders are again evaluated with the newly found receivers by solving \eqref{eqn-9} or \eqref{eqn-10}. The above procedure is repeated until \eqn{i \to \infty} or for some fixed \eqn{I_{\max}} as outlined in Algorithm \ref{algo-1}.

The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying the total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained using \ac{MMSE} receivers in \eqref{eqn-10}. Now, by using fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c} for all users.

%	consider modified objective \eqref{mod_obj} with a quadratic term instead of \eqref{eqn-6.1}. Moreover, we also bound \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq \beta_{\max}} for some large \eqn{\beta_{\max} \gg P_{\max}} without affecting the solution to ensure compactness of the feasible set, since \eqn{\beta_{l,k,n}} need not be bounded when \eqn{\gamma_{l,k,n} = 0}, \textit{i.e.}, when \eqn{\ith{l}} stream is inactive. Using these modifications, convergence of the sequence of iterates is discussed in Appendix \ref{sec-3.5}.}
\begin{comment}
